---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--
[![Travis-CI Build Status](https://travis-ci.org/MHenderson/funcgeo.svg?branch=master)](https://travis-ci.org/MHenderson/funcgeo)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/MHenderson/funcgeo?branch=master&svg=true)](https://ci.appveyor.com/project/MHenderson/funcgeo)
[![Coverage Status](https://img.shields.io/codecov/c/github/MHenderson/funcgeo/master.svg)](https://codecov.io/github/MHenderson/funcgeo?branch=master)
-->

# funcgeo

The goal of **funcgeo** is to reproduce, using R, all pictures from the
following two papers of Peter Henderson:

* [Henderson, P. (1982). *Functional Geometry*.](http://users.ecs.soton.ac.uk/peter/funcgeo.pdf)
* [Henderson, P. (2002). *Functional Geometry*.](http://eprints.soton.ac.uk/257577/1/funcgeo2.pdf)

## Installation

You can install **funcgeo** from my Drat repository on Github:

```R
# install.packages("drat")
drat::addRepo("MHenderson")
install.packages("funcgeo")
```

## Examples

```{r, message = FALSE, fig.width = 3, fig.height = 3}
library(funcgeo)

plot(cycle(rot(fish_q)))
```

```{r, message = FALSE, fig.width = 3, fig.height = 3}
plot(quartet(fish_p, fish_q, fish_r, fish_s))
```

```{r, message = FALSE, fig.width = 3, fig.height = 3}
plot(cycle(rot(fish_q)))
```

To save a picture as SVG, use the `svg` device.

```{r, eval = FALSE}
svg("fish.svg", width = 3, height = 3)
plot(quartet(fish_p, fish_q, fish_r, fish_s))
dev.off()
```

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
