---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![Travis-CI Build Status](https://travis-ci.org/MHenderson/funcgeo.svg?branch=master)](https://travis-ci.org/MHenderson/funcgeo)
[![Coverage Status](https://img.shields.io/codecov/c/github/MHenderson/funcgeo/master.svg)](https://codecov.io/github/MHenderson/funcgeo?branch=master)
[![Build status](https://ci.appveyor.com/api/projects/status/jwap9ayr8mviguc0?svg=true)](https://ci.appveyor.com/project/MHenderson/funcgeo)
[![DOI](https://zenodo.org/badge/72451164.svg)](https://zenodo.org/badge/latestdoi/72451164)

# funcgeo

The goal of **funcgeo** is to reproduce, using R, all pictures from the
following two papers of Peter Henderson:

* [Henderson, P. (1982). *Functional Geometry*.](http://users.ecs.soton.ac.uk/peter/funcgeo.pdf)
* [Henderson, P. (2002). *Functional Geometry*.](http://eprints.soton.ac.uk/257577/1/funcgeo2.pdf)

## Installation

You can install **funcgeo** from my Drat repository on Github:

```R
# install.packages("drat")
drat::addRepo("MHenderson")
install.packages("funcgeo")
```

## Examples

```{r, include = FALSE}
nill <- grid::nullGrob()
```


```{r, message = FALSE, fig.width = 5, fig.height = 5}
library(funcgeo)

t <- quartet(fish_p, fish_q, fish_r, fish_s)
u <- cycle(rot(fish_q))

side1 <- quartet(nill, nill, rot(t), t)
side2 <- quartet(side1, side1, rot(t), t)

corner1 <- quartet(nill, nill, nill, u)
corner2 <- quartet(corner1, side1, rot(side1), u)

corner <- nonet(
  corner2, side2, side2,
  rot(side2), u, rot(t),
  rot(side2), rot(t), rot(fish_q)
)

squarelimit <- cycle(corner)
plot(squarelimit)
```

To save a picture as SVG, use the `svg` device.

```{r, eval = FALSE}
svg("fish.svg", width = 3, height = 3)
plot(quartet(fish_p, fish_q, fish_r, fish_s))
dev.off()
```

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
